\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-09 fully-abstract-comp/popl2019/paper.tex
Typo.

By inspecting the operational semantics of \srccm{}, we can see that it does not allow reads from stack frames on the call stack which means that it insures LSE.
Further, the built-in call and returns make sure that a stack frame is pushed on call, and a return is to the address in the topmost stack frame on the call stack which means that we have WBCF.
In other words by inspection of the operational semantics, \srccm{} has LSE and WBCF.
It is important to point this out as \stktokens{} guarantee exactly the LSE and WBCF we have on \srccm{}.

>>>>

By inspecting the operational semantics of \srccm{}, we can see that it does not allow reads from stack frames on the call stack which means that it ensures LSE.
Further, the built-in call and returns make sure that a stack frame is pushed on call, and a return is to the address in the topmost stack frame on the call stack which means that we have WBCF.
In other words by inspection of the operational semantics, \srccm{} has LSE and WBCF.
It is important to point this out as \stktokens{} guarantee exactly the LSE and WBCF we have on \srccm{}.
